Time Series Bootstrapping For Solar Current

### 2021-12-08 deliverables/paper.Rmd
Bootstrap CIs and MC coverage estimate

```{r libs}
library(tidyverse)
library(boot)
```

```{r data}
df <- read_csv("../data/final/irradiance_full_final.csv")
```

@@

```{r timeseries}

@@

```{r filter}
HOUR_WINDOW <- 11:16
df_high_irradiance <- df[df$Hour %in% HOUR_WINDOW, ]
filtered_current_hist <- ggplot() +
  geom_histogram(aes(x = df_high_irradiance$current_out)) +
  theme_bw()
print(filtered_current_hist)
```

@@

mean_boot_plot <- ggplot(vis_df) +
  geom_histogram(aes(x = boot, y=..density.., fill = type), position = "identity", alpha = 0.5, color = "black") +
  xlab("Bootstrap sample means") +
  labs(fill = "Bootstrap type") +
  theme_bw()
ggsave("./images/mean_boot_plot.png", make_plot_for_pres(mean_boot_plot), width = 16, height = 12)
```

>>>>

```{r libs, include=FALSE, message=FALSE}
library(tidyverse)
library(boot)
```

```{r data, message=FALSE, warning=FALSE}
df <- read_csv("../data/final/irradiance_full_final.csv") %>%
  select(-'...1')
```

@@

```{r timeseries, warning=FALSE}

@@

```{r filter}
HOUR_WINDOW <- 11:16
df_high_irradiance <- df[df$Hour %in% HOUR_WINDOW, ]
filtered_current_hist <- ggplot() +
  geom_histogram(aes(x = df_high_irradiance$current_out, y = ..density..), binwidth = .0025) +
  theme_bw() +
  labs(title='Distribution of Current Outputs', subtitle='Restricted to high irradiance hours of the day', 
       x = 'Current Output', y = 'Density')
print(filtered_current_hist)
```

@@

# percentile bootstrap CI used
alpha <- .05
block_ci <- quantile(boot_block_df$boot, c(alpha / 2, 1 - alpha / 2))
iid_ci <- quantile(boot_iid_df$boot, c(alpha / 2, 1 - alpha / 2))

mean_boot_plot <- ggplot(vis_df) +
  geom_histogram(aes(x = boot, y = ..density.., fill = type), position = "identity", alpha = .5, color = "black", 
                 binwidth = .0001) +
  # geom_segment(aes(x = block_ci[1], xend = block_ci[2], y = 1250, yend = 1250), color = 'tomato', alpha = .01) +
  geom_vline(aes(xintercept = block_ci[1]), linetype = 'dashed', color = 'tomato', alpha = .5) +
  geom_vline(aes(xintercept = block_ci[2]), linetype = 'dashed', color = 'tomato', alpha = .5) +
  # geom_segment(aes(x = iid_ci[1], xend = iid_ci[2], y = 1300, yend = 1300), color = 'turquoise3', alpha = .01) +
  geom_vline(aes(xintercept = iid_ci[1]), linetype = 'dashed', color = 'turquoise3', alpha = .5) +
  geom_vline(aes(xintercept = iid_ci[2]), linetype = 'dashed', color = 'turquoise3', alpha = .5) +
  labs(fill = "Bootstrap Type", title='Bootstrapped Current Output', subtitle = 'Percentile confidence intervals given', 
       x = 'Bootstrap Sample Means', y = 'Density') +
  theme_bw()
ggsave("./images/mean_boot_plot.png", make_plot_for_pres(mean_boot_plot), width = 16, height = 12)
```

```{r}
# rough MC coverage estimate assuming dependent bootstrap distribution as a null
B <- 10000
n <- nrow(boot_block_df)

lower <- as.numeric(iid_ci[1])
upper <- as.numeric(iid_ci[2])

mu <- mean(boot_block_df$boot)
sigma <- sd(boot_block_df$boot)

sample <- rnorm(B, mu, sigma)

sum(sample >= lower & sample <= upper) / n
```
